\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-22 root.tex
clarified Fig 5, 9

Many systems perform trajectory planning over a sliding window within the full path which progresses with the vehicle.
This requires ... \textbf{something about computing actions through stop signs before it's necessary and how that's inefficient}.
We propose to break the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:segmentation}, and  execute them incrementally.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Segmentation of the path by path manager.
    The trajectory generation is serially called on each segment colored differently.
  }
  \label{fig:segmentation}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \subfigure[
    Clustering output for a short path when using an algorithm which draws segment boundaries around curves.
    Portions in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  ]{
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  % \subfigure[
  %   Showing the path projected onto the one dimensional s coordinate system
  % ]{
  %   \includegraphics[width=1.0\columnwidth]{graphics/1Dsegmentation.png}
  % }
  % \\
  \subfigure[
    Example of $v_m$ consolidation for simple univariate path clustering which corresponds to the path shown above.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  ]{
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Path segmentation and speed ceiling consolidation procedures.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

>>>>

Many systems perform trajectory planning over a sliding window within the full path which progresses with the vehicle.
This requires ... \textbf{something about computing actions through stop signs before it's necessary and how that's inefficient}.
We propose to break the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:subpathdivision}, and  execute them incrementally.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Dividing the path into subpaths at stop signs.
    The trajectory generation is serially called on each segment which is colored differently here.
  }
  \label{fig:subpathdivision}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \subfigure[
    Result of dividing a single subpath into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The subpath segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  ]{
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  % \subfigure[
  %   Showing the path projected onto the one dimensional s coordinate system
  % ]{
  %   \includegraphics[width=1.0\columnwidth]{graphics/1Dsegmentation.png}
  % }
  % \\
  \subfigure[
    Example of how the subpath's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  ]{
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}
